\textsc{Second-order state-constraint Hamilton-Jacobi equations}

### 2021-01-09 Drafts and notes/draft_01.tex
Updating the tex file, xing all warnings and errors.
change font to mathpazo

\usepackage[utf8]{inputenc}
\usepackage[euler-digits]{eulervm}
%\usepackage[bitstream-charter]{mathdesign}
\usepackage{eucal}
\usepackage[unicode=true]{hyperref}
\hypersetup{colorlinks = true,pdftex}
%\hypersetup{hidelinks=true}
\hypersetup{
     colorlinks,
     linkcolor={black!50!black},
	% linkcolor={red!50!black},
%    linkbordercolor = {blue},
%    <your other options...>,
     citecolor={blue}
}

@@

\usepackage{geometry}
\geometry{verbose,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2.5cm,headheight=2.5cm}

@@

\title[Rate of convergence]
{Second-order state-constraint Hamilton-Jacobi equations}

@@

\section{Introduction}\label{sec:intro}

>>>>

\usepackage[utf8]{inputenc}
\usepackage{mathpazo}
\usepackage[euler-digits]{eulervm}
%\usepackage[bitstream-charter]{mathdesign}
\usepackage{eucal}
\usepackage[unicode=true]{hyperref}
\hypersetup{colorlinks = true}
%\hypersetup{hidelinks=true}
\hypersetup{
     colorlinks,
     linkcolor={black!50!black},
	% linkcolor={red!50!black},
%    linkbordercolor = {blue},
%    <your other options...>,
     citecolor={blue}
}

@@

\usepackage{geometry}
%\geometry{verbose,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2.5cm,headheight=2.5cm}

@@

\title[Rate of convergence]
{\textsc{Second-order state-constraint Hamilton-Jacobi equations}}

@@

\section{Introduction}\label{sec:intro}
Paper to read \cite{Ishii2017a}.
